Storm surge modelling in the Strait of Georgia

### 2014-10-14 RoughWork/manuscript.tex
Updated comments on tide-surge interaction

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/feb2006_factors.pdf}
\caption{Comparison of the modelled residual for three simulations: A simulation with all forcing (solid black), a simulation without atmospheric forcing (solid grey), a simulation without the sea surface height anomaly (dashed black) and a simulation with only wind forcing, i.e.\ no sea surface height anomaly or pressure (dashed grey). }
\label{fig:factors}
\end{figure}

Finally, an assessment of the importance of including the tide-surge interaction is presented next. A simulation of the surge propagation without including any tidal forcing is compared with the modelled residual in Figure \ref{fig:tidesurge}.  Recall, the modelled residual is defined as the difference between the sea surface height in a simulation with all forcing and a simulation with tides and rivers only. A comparison between the modelled residual and a surge-only run can determine the significance of the tide-surge interaction. The most significant differences occur at Point Atkinson where the maximum of the surge-only case is 8.6 cm higher than maximum modelled residual.  In contrast, the tide-surge interaction at Victoria is hardly noticeable. Indeed, a spatial map of the difference between the modelled residual and surge-only difference (not shown here) indicates that the tide-surge interaction is more pronounced after the San Juan and Gulf Islands. The passages between these islands are known for vigorous tidal mixing, which may have an effect on the surge propagation. However, the effect is a relatively small overestimate of the surge elevation and no changes to the timing of the surge. So, in operational settings, performing a surge-only simulation and adding the predicted tides a posteriori could be more computationally efficient with only a small decrease in the accuracy of the prediction.

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/feb2006_factors.pdf}
\caption{Comparison of the modelled residual for four simulations: A simulation with all forcing (solid black), a simulation without atmospheric forcing (solid grey), a simulation without the sea surface height anomaly (dashed black) and a simulation with only wind forcing, i.e.\ no sea surface height anomaly or pressure (dashed grey). }
\label{fig:factors}
\end{figure}

Finally, an assessment of the importance of including the tide-surge interaction is presented next. A simulation of the surge propagation without including any tidal forcing is compared with the modelled residual in Figure \ref{fig:tidesurge}.  Recall, the modelled residual is defined as the difference between the sea surface height in a simulation with all forcing and a simulation with tides and rivers only. A comparison between the modelled residual and a surge-only run can determine the significance of the tide-surge interaction. The most significant differences occur at Point Atkinson where the maximum of the surge-only case is 8.7 cm higher than maximum modelled residual, about 10\% higher of the surge amplitude.  In contrast, the tide-surge interaction at Victoria is hardly noticeable. Indeed, a spatial map of the difference between the modelled residual and surge-only difference (not shown here) indicates that the tide-surge interaction is more pronounced after the San Juan and Gulf Islands. The passages between these islands are known for vigorous tidal mixing, which may have a nonlinear effect on the surge propagation. However, the effect is a relatively small overestimate of the surge elevation and no changes to the timing of the surge. So, in operational settings, performing a surge-only simulation and adding the predicted tides a posteriori could be more computationally efficient with only a small decrease in the accuracy of the prediction.
